We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-05-08 paper/paper.tex
updated tex

\bibliographystyle{mnras}
\bibliography{Dwarfs}

>>>>

\bibliographystyle{mnras}
%\bibliography{Dwarfs}

\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

\bibitem[\protect\citeauthoryear{{Ahmed}, {Brooks}  \& {Christensen}}{{Ahmed}
  et~al.}{2017}]{2017MNRAS.466.3119A}
{Ahmed} S.~H.,  {Brooks} A.~M.,   {Christensen} C.~R.,  2017, \mn@doi [\mnras]
  {10.1093/mnras/stw3271}, \href
  {http://adsabs.harvard.edu/abs/2017MNRAS.466.3119A} {466, 3119}

\bibitem[\protect\citeauthoryear{{Boylan-Kolchin}, {Bullock}  \&
  {Kaplinghat}}{{Boylan-Kolchin} et~al.}{2011}]{2011MNRAS.415L..40B}
{Boylan-Kolchin} M.,  {Bullock} J.~S.,   {Kaplinghat} M.,  2011, \mn@doi
  [\mnras] {10.1111/j.1745-3933.2011.01074.x}, \href
  {http://adsabs.harvard.edu/abs/2011MNRAS.415L..40B} {415, L40}

\bibitem[\protect\citeauthoryear{{Bryan}, {Kay}, {Duffy}, {Schaye}, {Dalla
  Vecchia}  \& {Booth}}{{Bryan} et~al.}{2013}]{2013MNRAS.429.3316B}
{Bryan} S.~E.,  {Kay} S.~T.,  {Duffy} A.~R.,  {Schaye} J.,  {Dalla Vecchia} C.,
    {Booth} C.~M.,  2013, \mn@doi [\mnras] {10.1093/mnras/sts587}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.429.3316B} {429, 3316}

\bibitem[\protect\citeauthoryear{{Buck}, {Macci{\`o}}  \& {Dutton}}{{Buck}
  et~al.}{2015}]{2015ApJ...809...49B}
{Buck} T.,  {Macci{\`o}} A.~V.,   {Dutton} A.~A.,  2015, \mn@doi [\apj]
  {10.1088/0004-637X/809/1/49}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...809...49B} {809, 49}

\bibitem[\protect\citeauthoryear{{Buck}, {Dutton}  \& {Macci{\`o}}}{{Buck}
  et~al.}{2016}]{2016MNRAS.460.4348B}
{Buck} T.,  {Dutton} A.~A.,   {Macci{\`o}} A.~V.,  2016, \mn@doi [\mnras]
  {10.1093/mnras/stw1232}, \href
  {http://adsabs.harvard.edu/abs/2016MNRAS.460.4348B} {460, 4348}

\bibitem[\protect\citeauthoryear{{Busha}, {Wechsler}, {Behroozi}, {Gerke},
  {Klypin}  \& {Primack}}{{Busha} et~al.}{2011}]{2011ApJ...743..117B}
{Busha} M.~T.,  {Wechsler} R.~H.,  {Behroozi} P.~S.,  {Gerke} B.~F.,  {Klypin}
  A.~A.,   {Primack} J.~R.,  2011, \mn@doi [\apj]
  {10.1088/0004-637X/743/2/117}, \href
  {http://adsabs.harvard.edu/abs/2011ApJ...743..117B} {743, 117}

\bibitem[\protect\citeauthoryear{{Cautun} \& {Frenk}}{{Cautun} \&
  {Frenk}}{2017}]{2017MNRAS.468L..41C}
{Cautun} M.,  {Frenk} C.~S.,  2017, \mn@doi [\mnras] {10.1093/mnrasl/slx025},
  \href {http://adsabs.harvard.edu/abs/2017MNRAS.468L..41C} {468, L41}

\bibitem[\protect\citeauthoryear{{Cautun}, {Bose}, {Frenk}, {Guo}, {Han},
  {Hellwing}, {Sawala}  \& {Wang}}{{Cautun} et~al.}{2015}]{2015MNRAS.452.3838C}
{Cautun} M.,  {Bose} S.,  {Frenk} C.~S.,  {Guo} Q.,  {Han} J.,  {Hellwing}
  W.~A.,  {Sawala} T.,   {Wang} W.,  2015, \mn@doi [\mnras]
  {10.1093/mnras/stv1557}, \href
  {http://adsabs.harvard.edu/abs/2015MNRAS.452.3838C} {452, 3838}

\bibitem[\protect\citeauthoryear{{Collins} et~al.,}{{Collins}
  et~al.}{2015}]{2015ApJ...799L..13C}
{Collins} M.~L.~M.,  et~al., 2015, \mn@doi [\apjl]
  {10.1088/2041-8205/799/1/L13}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...799L..13C} {799, L13}

\bibitem[\protect\citeauthoryear{{Conn} et~al.,}{{Conn}
  et~al.}{2013}]{2013ApJ...766..120C}
{Conn} A.~R.,  et~al., 2013, \mn@doi [\apj] {10.1088/0004-637X/766/2/120},
  \href {http://adsabs.harvard.edu/abs/2013ApJ...766..120C} {766, 120}

\bibitem[\protect\citeauthoryear{{Conroy}, {Wechsler}  \& {Kravtsov}}{{Conroy}
  et~al.}{2006}]{2006ApJ...647..201C}
{Conroy} C.,  {Wechsler} R.~H.,   {Kravtsov} A.~V.,  2006, \mn@doi [\apj]
  {10.1086/503602}, \href {http://adsabs.harvard.edu/abs/2006ApJ...647..201C}
  {647, 201}

\bibitem[\protect\citeauthoryear{{Fernando}, {Arias}, {Guglielmo}, {Lewis},
  {Ibata}  \& {Power}}{{Fernando} et~al.}{2017}]{2017MNRAS.465..641F}
{Fernando} N.,  {Arias} V.,  {Guglielmo} M.,  {Lewis} G.~F.,  {Ibata} R.~A.,
  {Power} C.,  2017, \mn@doi [\mnras] {10.1093/mnras/stw2694}, \href
  {http://adsabs.harvard.edu/abs/2017MNRAS.465..641F} {465, 641}

\bibitem[\protect\citeauthoryear{{Forero-Romero} \&
  {Gonz{\'a}lez}}{{Forero-Romero} \&
  {Gonz{\'a}lez}}{2015}]{2015ApJ...799...45F}
{Forero-Romero} J.~E.,  {Gonz{\'a}lez} R.,  2015, \mn@doi [\apj]
  {10.1088/0004-637X/799/1/45}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...799...45F} {799, 45}

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Yepes},
  {Gottl{\"o}ber}, {Piontek}, {Klypin}  \& {Steinmetz}}{{Forero-Romero}
  et~al.}{2011}]{2011MNRAS.417.1434F}
{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Yepes} G.,  {Gottl{\"o}ber} S.,
  {Piontek} R.,  {Klypin} A.,   {Steinmetz} M.,  2011, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2011.19358.x}, \href
  {http://adsabs.harvard.edu/abs/2011MNRAS.417.1434F} {417, 1434}

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Bustamante},
  {Gottl{\"o}ber}  \& {Yepes}}{{Forero-Romero} et~al.}{2013}]{ForeroRomero2013}
{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Bustamante} S.,  {Gottl{\"o}ber} S.,
  {Yepes} G.,  2013, \mn@doi [\apjl] {10.1088/2041-8205/767/1/L5}, \href
  {http://adsabs.harvard.edu/abs/2013ApJ...767L...5F} {767, L5}

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras}  \&
  {Padilla}}{{Forero-Romero} et~al.}{2014}]{2014MNRAS.443.1090F}
{Forero-Romero} J.~E.,  {Contreras} S.,   {Padilla} N.,  2014, \mn@doi [\mnras]
  {10.1093/mnras/stu1150}, \href
  {http://adsabs.harvard.edu/abs/2014MNRAS.443.1090F} {443, 1090}

\bibitem[\protect\citeauthoryear{{Garrison-Kimmel}, {Boylan-Kolchin}, {Bullock}
   \& {Lee}}{{Garrison-Kimmel} et~al.}{2014}]{2014MNRAS.438.2578G}
{Garrison-Kimmel} S.,  {Boylan-Kolchin} M.,  {Bullock} J.~S.,   {Lee} K.,
  2014, \mn@doi [\mnras] {10.1093/mnras/stt2377}, \href
  {http://adsabs.harvard.edu/abs/2014MNRAS.438.2578G} {438, 2578}

\bibitem[\protect\citeauthoryear{{Gillet}, {Ocvirk}, {Aubert}, {Knebe},
  {Libeskind}, {Yepes}, {Gottl{\"o}ber}  \& {Hoffman}}{{Gillet}
  et~al.}{2015}]{2015ApJ...800...34G}
{Gillet} N.,  {Ocvirk} P.,  {Aubert} D.,  {Knebe} A.,  {Libeskind} N.,  {Yepes}
  G.,  {Gottl{\"o}ber} S.,   {Hoffman} Y.,  2015, \mn@doi [\apj]
  {10.1088/0004-637X/800/1/34}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...800...34G} {800, 34}

\bibitem[\protect\citeauthoryear{{Guo}, {White}, {Li}  \&
  {Boylan-Kolchin}}{{Guo} et~al.}{2010}]{2010MNRAS.404.1111G}
{Guo} Q.,  {White} S.,  {Li} C.,   {Boylan-Kolchin} M.,  2010, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2010.16341.x}, \href
  {http://adsabs.harvard.edu/abs/2010MNRAS.404.1111G} {404, 1111}

\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
  et~al.}{2013}]{2013ApJS..208...19H}
{Hinshaw} G.,  et~al., 2013, \mn@doi [\apjs] {10.1088/0067-0049/208/2/19},
  \href {http://adsabs.harvard.edu/abs/2013ApJS..208...19H} {208, 19}

\bibitem[\protect\citeauthoryear{{Ibata} et~al.,}{{Ibata}
  et~al.}{2013}]{2013Natur.493...62I}
{Ibata} R.~A.,  et~al., 2013, \mn@doi [\nat] {10.1038/nature11717}, \href
  {http://adsabs.harvard.edu/abs/2013Natur.493...62I} {493, 62}

\bibitem[\protect\citeauthoryear{{Koch} \& {Grebel}}{{Koch} \&
  {Grebel}}{2006}]{2006AJ....131.1405K}
{Koch} A.,  {Grebel} E.~K.,  2006, \mn@doi [\aj] {10.1086/499534}, \href
  {http://adsabs.harvard.edu/abs/2006AJ....131.1405K} {131, 1405}

\bibitem[\protect\citeauthoryear{{Kravtsov}, {Berlind}, {Wechsler}, {Klypin},
  {Gottl{\"o}ber}, {Allgood}  \& {Primack}}{{Kravtsov}
  et~al.}{2004}]{2004ApJ...609...35K}
{Kravtsov} A.~V.,  {Berlind} A.~A.,  {Wechsler} R.~H.,  {Klypin} A.~A.,
  {Gottl{\"o}ber} S.,  {Allgood} B.,   {Primack} J.~R.,  2004, \mn@doi [\apj]
  {10.1086/420959}, \href {http://adsabs.harvard.edu/abs/2004ApJ...609...35K}
  {609, 35}

\bibitem[\protect\citeauthoryear{{Kroupa}, {Theis}  \& {Boily}}{{Kroupa}
  et~al.}{2005}]{2005A&A...431..517K}
{Kroupa} P.,  {Theis} C.,   {Boily} C.~M.,  2005, \mn@doi [\aap]
  {10.1051/0004-6361:20041122}, \href
  {http://adsabs.harvard.edu/abs/2005A%26A...431..517K} {431, 517}

\bibitem[\protect\citeauthoryear{{Kunkel} \& {Demers}}{{Kunkel} \&
  {Demers}}{1976}]{1976RGOB..182..241K}
{Kunkel} W.~E.,  {Demers} S.,  1976, in {Dickens} R.~J.,  {Perry} J.~E.,
  {Smith} F.~G.,   {King} I.~R.,  eds,  Royal Greenwich Observatory Bulletins
  Vol. 182, The Galaxy and the Local Group. p.~241

\bibitem[\protect\citeauthoryear{{Libeskind}, {Frenk}, {Cole}, {Helly},
  {Jenkins}, {Navarro}  \& {Power}}{{Libeskind}
  et~al.}{2005}]{2005MNRAS.363..146L}
{Libeskind} N.~I.,  {Frenk} C.~S.,  {Cole} S.,  {Helly} J.~C.,  {Jenkins} A.,
  {Navarro} J.~F.,   {Power} C.,  2005, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2005.09425.x}, \href
  {http://adsabs.harvard.edu/abs/2005MNRAS.363..146L} {363, 146}

\bibitem[\protect\citeauthoryear{{Libeskind}, {Frenk}, {Cole}, {Jenkins}  \&
  {Helly}}{{Libeskind} et~al.}{2009}]{2009MNRAS.399..550L}
{Libeskind} N.~I.,  {Frenk} C.~S.,  {Cole} S.,  {Jenkins} A.,   {Helly} J.~C.,
  2009, \mn@doi [\mnras] {10.1111/j.1365-2966.2009.15315.x}, \href
  {http://adsabs.harvard.edu/abs/2009MNRAS.399..550L} {399, 550}

\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Tully}, {Courtois},
  {Pomar{\`e}de}, {Gottl{\"o}ber}  \& {Steinmetz}}{{Libeskind}
  et~al.}{2015}]{2015MNRAS.452.1052L}
{Libeskind} N.~I.,  {Hoffman} Y.,  {Tully} R.~B.,  {Courtois} H.~M.,
  {Pomar{\`e}de} D.,  {Gottl{\"o}ber} S.,   {Steinmetz} M.,  2015, \mn@doi
  [\mnras] {10.1093/mnras/stv1302}, \href
  {http://adsabs.harvard.edu/abs/2015MNRAS.452.1052L} {452, 1052}

\bibitem[\protect\citeauthoryear{{Lynden-Bell}}{{Lynden-Bell}}{1976}]{1976MNRAS.174..695L}
{Lynden-Bell} D.,  1976, \mn@doi [\mnras] {10.1093/mnras/174.3.695}, \href
  {http://adsabs.harvard.edu/abs/1976MNRAS.174..695L} {174, 695}

\bibitem[\protect\citeauthoryear{{McConnachie}}{{McConnachie}}{2012}]{2012AJ....144....4M}
{McConnachie} A.~W.,  2012, \mn@doi [\aj] {10.1088/0004-6256/144/1/4}, \href
  {http://adsabs.harvard.edu/abs/2012AJ....144....4M} {144, 4}

\bibitem[\protect\citeauthoryear{{Metz}, {Kroupa}  \& {Jerjen}}{{Metz}
  et~al.}{2007}]{2007MNRAS.374.1125M}
{Metz} M.,  {Kroupa} P.,   {Jerjen} H.,  2007, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2006.11228.x}, \href
  {http://adsabs.harvard.edu/abs/2007MNRAS.374.1125M} {374, 1125}

\bibitem[\protect\citeauthoryear{{Pawlowski} \& {McGaugh}}{{Pawlowski} \&
  {McGaugh}}{2014}]{2014ApJ...789L..24P}
{Pawlowski} M.~S.,  {McGaugh} S.~S.,  2014, \mn@doi [\apjl]
  {10.1088/2041-8205/789/1/L24}, \href
  {http://adsabs.harvard.edu/abs/2014ApJ...789L..24P} {789, L24}

\bibitem[\protect\citeauthoryear{{Pawlowski}, {Kroupa}  \&
  {Jerjen}}{{Pawlowski} et~al.}{2013}]{2013MNRAS.435.1928P}
{Pawlowski} M.~S.,  {Kroupa} P.,   {Jerjen} H.,  2013, \mn@doi [\mnras]
  {10.1093/mnras/stt1384}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P} {435, 1928}

\bibitem[\protect\citeauthoryear{{Pawlowski}, {Kroupa}  \&
  {Jerjen}}{{Pawlowski} et~al.}{2014}]{2014yCat..74351928P}
{Pawlowski} M.~S.,  {Kroupa} P.,   {Jerjen} H.,  2014, VizieR Online Data
  Catalog, \href {http://adsabs.harvard.edu/abs/2014yCat..74351928P} {743}

\bibitem[\protect\citeauthoryear{{Pawlowski}, {Famaey}, {Merritt}  \&
  {Kroupa}}{{Pawlowski} et~al.}{2015}]{2015ApJ...815...19P}
{Pawlowski} M.~S.,  {Famaey} B.,  {Merritt} D.,   {Kroupa} P.,  2015, \mn@doi
  [\apj] {10.1088/0004-637X/815/1/19}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...815...19P} {815, 19}

\bibitem[\protect\citeauthoryear{{Pawlowski} et~al.,}{{Pawlowski}
  et~al.}{2017}]{2017AN....338..854P}
{Pawlowski} M.~S.,  et~al., 2017, \mn@doi [Astronomische Nachrichten]
  {10.1002/asna.201713366}, \href
  {http://adsabs.harvard.edu/abs/2017AN....338..854P} {338, 854}

\bibitem[\protect\citeauthoryear{{Pillepich} et~al.,}{{Pillepich}
  et~al.}{2018}]{2018MNRAS.473.4077P}
{Pillepich} A.,  et~al., 2018, \mn@doi [\mnras] {10.1093/mnras/stx2656}, \href
  {http://adsabs.harvard.edu/abs/2018MNRAS.473.4077P} {473, 4077}

\bibitem[\protect\citeauthoryear{{Sawala} et~al.,}{{Sawala}
  et~al.}{2016}]{2016MNRAS.457.1931S}
{Sawala} T.,  et~al., 2016, \mn@doi [\mnras] {10.1093/mnras/stw145}, \href
  {http://adsabs.harvard.edu/abs/2016MNRAS.457.1931S} {457, 1931}

\bibitem[\protect\citeauthoryear{{Springel}}{{Springel}}{2010}]{2010MNRAS.401..791S}
{Springel} V.,  2010, \mn@doi [\mnras] {10.1111/j.1365-2966.2009.15715.x},
  \href {http://adsabs.harvard.edu/abs/2010MNRAS.401..791S} {401, 791}

\bibitem[\protect\citeauthoryear{{Starkenburg} et~al.,}{{Starkenburg}
  et~al.}{2013}]{2013MNRAS.429..725S}
{Starkenburg} E.,  et~al., 2013, \mn@doi [\mnras] {10.1093/mnras/sts367}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.429..725S} {429, 725}

\bibitem[\protect\citeauthoryear{{Vogelsberger} et~al.,}{{Vogelsberger}
  et~al.}{2014}]{2014MNRAS.444.1518V}
{Vogelsberger} M.,  et~al., 2014, \mn@doi [\mnras] {10.1093/mnras/stu1536},
  \href {http://adsabs.harvard.edu/abs/2014MNRAS.444.1518V} {444, 1518}

\bibitem[\protect\citeauthoryear{{Wang}, {Frenk}  \& {Cooper}}{{Wang}
  et~al.}{2013}]{2013MNRAS.429.1502W}
{Wang} J.,  {Frenk} C.~S.,   {Cooper} A.~P.,  2013, \mn@doi [\mnras]
  {10.1093/mnras/sts442}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.429.1502W} {429, 1502}

\bibitem[\protect\citeauthoryear{{Zentner}, {Kravtsov}, {Gnedin}  \&
  {Klypin}}{{Zentner} et~al.}{2005}]{2005ApJ...629..219Z}
{Zentner} A.~R.,  {Kravtsov} A.~V.,  {Gnedin} O.~Y.,   {Klypin} A.~A.,  2005,
  \mn@doi [\apj] {10.1086/431355}, \href
  {http://adsabs.harvard.edu/abs/2005ApJ...629..219Z} {629, 219}

\makeatother
\end{thebibliography}
